Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Small fixes to building the data set section
Start adding info regarding API rate limits for GCP and Microsoft Azure

Throughout the entire application, we tried to apply the UNIX philosophy of creating small applications that do one thing, but 
do it well. Therefore, we implemented clean and simple packages where we tried to use the standard library as much as possible
so that potential contributors coming to the project would find it easy to start working directly on the code. Also, we designed 
the tool with extensibility in mind, so that other database providers (e.g. CockroachDB) or issue tracking systems (e.g. Bugzilla) 
could be easily implemented - this was achieved using the elegant Go interfaces.

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. Then, it runs in parallel the \emph{seven types of analysis}:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket;
  \item \emph{stack traces} - runs complex regex for detecting stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  having many words or comments decreases or increases Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 is completely negative, 1 is completely 
  positive).
\end{itemize}

>>>>

Throughout the entire application, we tried to apply the UNIX philosophy of creating small applications that do one thing, but 
do it well. Therefore, we implemented clean and simple packages where we tried to use the standard library as much as possible
so that potential contributors coming to the project would find it easy to start working directly on the code. Also, we designed 
the tool with extensibility in mind, so that other database providers (e.g. CockroachDB) or issue tracking systems (e.g. Bugzilla) 
could be easily implemented - this was achieved using the elegant Go interfaces and the idea of composition.

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. Then, it runs in parallel the \emph{seven types of analysis}:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket;
  \item \emph{stack traces} - runs complex regex for detecting stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  having many words or comments decreases or increases Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

We hit several issues when working with Google Cloud Platform and Bing Spell
